% Created by Alexander Baker, original repo here: https://github.com/AlexLBaker/LaTeX-Resume

\documentclass[letterpaper]{cream_class}

\begin{document}

\header{Alexander Logan Baker}
       {Director of Data Analytics}
       {name@email.com}
       {+1 (123) 456-7890}
       {LinkedIn.com/alexander-l-baker}
       {GitHub.com/AlexLBaker}
       {123 North St, Indianapolis, IN 46200}

% About me
\noindent\textcolor{burgundy}{\textbf{\large About Me:}}

Data analytics professional, willing to relocate for the right opportunity. Seeking to expand skills in data science.

\vspace{6pt}
\hrule
\vspace{6pt}

% Technical Skills
\noindent\textcolor{burgundy}{\textbf{\large Technical Skills:}}
\vspace{-6pt}
\begin{itemize}[noitemsep, leftmargin=*]
      \item \textbf{Programming:} Python, Java, R, SQL, HTML, CSS, Javascript, \& TeX. Data science, analytics, web scraping \& development.
      \item \textbf{Database Management:} SSMS, AWS RDS, Power BI, mySQL, \& PostgreSQL. Relational databases, \& information schemas.
      \item \textbf{Modeling:} Machine learning, optimization, linear \& nonlinear programs, series forecasting, financial engineering \& modeling.
      \item \textbf{Data Visualization \& Excel:} Power BI, Tableau, Excel, Python, Java, \& R. Advanced Excel, vlookup, pivot tables \& charts.
      \item \textbf{Cloud Computing:} AWS EC2, Lambda, MS Azure, \& GitHub Codespace. Linux CLI, server data lakes, marts \& flows.
      \item \textbf{Project Management:} Microsoft Project \& Smartsheet. Management \& development in Waterfall, Agile, Kanban, \& Scrum.
      \item \textbf{Frameworks:} numpy, pandas, seaborn, matplotlib, yfinance, SQLalchemy, pytorch, jupyter, dplyr, ggplot2, shiny, \& hadoop.
    \end{itemize}      
  \hrule
  \vspace{6pt}
  
% Education
\noindent\textcolor{burgundy}{\noindent\textbf{\large Education:}\\[-3ex]}
\vspace{-3pt}
\begin{itemize}[noitemsep, leftmargin=*]
  \item {\large\textbf{Master of Science, Business Analytics and Information Management}} \hfill West Lafayette, IN \\
        \textbf{Purdue University, Daniels School of Business} \hfill June 2022 - May 2023
    \begin{itemize}[noitemsep, leftmargin=*]
      \item Program ranking 6th in the U.S. for Business Analytics. Concentration in financial analytics, data science, \& computer science.
    \end{itemize}
  \item {\large\textbf{Bachelor of Science, Physics}} \hfill Bloomington, IN \\
        \textbf{Indiana University, College of Arts \& Sciences} \hfill August 2018 - May 2022
    \begin{itemize}[noitemsep, leftmargin=*]
      \item Mathematics minor, physics research assistant, coursework concentration in statistics, information science, \& computer science.
    \end{itemize}
\end{itemize}
\hrule
\vspace{6pt}

% Experience
\noindent\textcolor{burgundy}{\noindent\textbf{\large Experience:}\\[-3ex]}
\vspace{-3pt}
\begin{itemize}[noitemsep, leftmargin=*]
  \item {\large\textbf{Director of Data Analytics, Strategic Enrollment \& Partnerships}} \hfill Indianapolis, IN \\
        \textbf{Indiana Wesleyan University} — employee \hfill August 2023 - present
    \begin{itemize}[noitemsep, leftmargin=*]
      \item Database management of data lake with Microsoft SSMS, \& Power BI data visualization. Project Management in Smartsheet.
      \item Data science with prediction models, logistic multiple regression, \& linear programming.
      \item Tools \& technologies: Python, R, Java, SQL, Excel, Power BI, Azure, Smartsheet, Salesforce
    \end{itemize}    
  \item {\large\textbf{Financial Analyst}} \hfill Greenfield, IN \\
        \textbf{Elanco Animal Health Inc.} — intern \hfill January 2023 - April 2023
    \begin{itemize}[noitemsep, leftmargin=*]
      \item Analyzed financial derivatives, with the high cost of hedge forward contracts in the forex hedging strategy of the balance sheet.
      \item Programmed heuristic optimization algorithm estimating optimal hedge ratios, for an 81\% reduction in forex exposure losses.
      \item Tools \& technologies: R, Python, VBA, advanced Excel, Monte Carlo simulations, nonlinear programming, \& optimization.
    \end{itemize}        
  \item {\large\textbf{Accounting Administrative Assistant}} \hfill Indianapolis, IN \\
            \textbf{Beam, Longest \& Neff LLC} — employee \hfill May 2021 - September 2021
    \begin{itemize}[noitemsep, leftmargin=*]
      \item Accounting for the wildfire relief project. Managed project database of spreadsheets, ICS 214s, laboratory reports, and backups.
      \item Tools \& technologies: Acrobat secure signatures, advanced Excel, VLOOKUP, Pivot Tables, Pivot Charts, \& data visualization.
    \end{itemize}    
  \item {\large\textbf{Laboratory Assistant}} \hfill Bloomington, IN \\
        \textbf{Indiana University Department of Physics} — employee \hfill August 2019 - May 2022
    \begin{itemize}[noitemsep, leftmargin=*]
      \item Lab preparation, maintained database of laboratory equipment, spare parts, manuals, and damaged equipment registry.
    \end{itemize}
\end{itemize}
  \hrule
  \vspace{6pt}
  
% Projects
\noindent\textcolor{burgundy}{\noindent\textbf{\large Projects:}\\[-3ex]}
\vspace{-3pt}
\begin{itemize}[noitemsep, leftmargin=*, itemsep=1pt]
    \item \textbf{\large Fama \& French Five-Factor Program} -- Financial Modeling \hfill February 2023 - August 2023
    \begin{itemize}[noitemsep, leftmargin=*, itemsep=1pt]
      \item Python program valuing securities as the risk premium over the model estimation found by ordinary least squares regression.
      \end{itemize}
    \item \textbf{\large Wedding Registration Website} -- Web Development \hfill August 2023 - present
    \begin{itemize}[noitemsep, leftmargin=*, itemsep=1pt]
      \item Developed website with HTML, CSS, \& Javascript for wedding registration and information.
      \end{itemize}
    \item \textbf{\large Allan Variance of Wattage Program} -- Research Assistant, Dr. Phil Richerme \hfill August 2021 - May 2022
    \begin{itemize}[noitemsep, leftmargin=*, itemsep=1pt]
      \item Python program for live Allan variance calculation of laser wattage, testing laser power output consistency for Doppler cooling.
    \end{itemize}
\end{itemize}     
  \hrule
  \vspace{6pt}
  
% Certifications
\noindent\textcolor{burgundy}{\noindent\textbf{\large Certifications:}\\[-3ex]}
\vspace{-3pt}
\begin{itemize}[noitemsep, leftmargin=*, itemsep=1pt]
  \item \textbf{\large AWS Certified Cloud Practitioner} -- issued by Amazon Web Services \hfill October 2022 - October 2027
  \item \textbf{\large \href{https://bcert.me/skzxpjuux}{Associate Certified Analytics Professional (aCAP)}} -- issued by INFORMS \hfill July 2023 - July 2026
  \item \textbf{\large Machine Learning Scientist with Python} -- issued by Datacamp \hfill February 2023
\end{itemize}   

\end{document}
